title

### 2013-02-04 paper.tex
ROAR

Our projections suggest that water shortages could indeed be a very significant problem leading up to 2025, in two significant ways:
On one hand, we predict that the overall water demand in the country will increase by several billion gallons per day. We will attempt to solve this problem of total water supply by constructing additional 
de-salinization plants and reservoirs. To decide where to build these, 
The more significant problem however, as was the case in the drought of 2012-2013, is that even when there is enough water flowing in the United States as a whole, it might be the case that one city is flooding with water, while another is in drought.
The obvious solution here is a means of moving water across the country, and this can be accomplished by constructing a network of pipelines.

@@

@@

Due to the scale and complexity of the task of water management in
the United States, we make several simplifying assumptions in order
to obtain a workable model.
\begin{itemize}
\item Counties are thought of as discrete entities, occupying points in
space located at their centroid. This assumption enables us to think
of counties as vertices (as in a graph). This assumption can be made
without losing too much accuracy for several reasons: The United States
is split into more than 3,000 counties, with an average area of less
than 3,300 square kilometers, and average length across of less than
60 kilometers. The level of inaccuracy is sufficiently low that it
is workable (in contrast, states for instance are far too large to
be accurately modeled as points).
\item When considering the costs of pipelines, only the distance of pipeline
is considered. The landscape of a region may in practice affect the
length of pipeline required, or may result in additional cost per
length of pipeline, but we shall not model this, as we could not find
data on the difficulty of pipeline construction across different types
of terrain.
\item Pipelines are thought of as bi-directional. This assumption essentially
reflects the reality of pipelines. There are a few exceptional cases
where it is significantly more difficult to send water in one direction,
but these are rare enough that they can be disregarded.
\item Pipelines have variable rates of water transmission, depending on
factors such as size. However, pipelines typically 
\item Some pipelines exist
\end{itemize}

@@

This model

>>>>

Our projections suggest that water shortages could indeed be a very significant problem leading up to 2025, in two significant ways:
On one hand, we predict that the overall water demand in the country will increase by several billion gallons per day. We will attempt to solve this problem of total water supply by constructing additional 
de-salinization plants and reservoirs. We build these in the places that have the greatest predicted increase in their water demands.
The more significant problem however, as was the case in the drought of 2012-2013, is that even when there is enough water flowing in the United States as a whole, it might be the case that one city is flooding with water, while another is in drought.
The obvious solution here is a means of moving water across the country, and this can be accomplished by constructing a network of pipelines.

@@

Compared to other analyses of the United States' fresh water supply, we believe that our paper provides some of the most useful results and recommendations, by focusing on the problem of fresh water being unevenly distributed across the country, rather than the problem of the United States as a whole lacking fresh water supplies.
Water management is a serious issue facing this country, and we strongly recommend that the government act in response to our findings.

@@

Due to the scale and complexity of the task of water management in
the United States, we make several simplifying assumptions in order
to obtain a workable model.
\begin{itemize}
\item Counties are thought of as discrete entities, occupying points in
space located at their centroid. This assumption enables us to think
of counties as vertices (as in a graph). This assumption can be made
without losing too much accuracy for several reasons: The United States
is split into more than 3,000 counties, with an average area of less
than 3,300 square kilometers, and average length across of less than
60 kilometers. The level of inaccuracy is sufficiently low that it
is workable (in contrast, states for instance are far too large to
be accurately modeled as points).
\item When considering the costs of pipelines, only the distance of pipeline
is considered. The landscape of a region may in practice affect the
length of pipeline required, or may result in additional cost per
length of pipeline, but we shall not model this, as we could not find
data on the difficulty of pipeline construction across different types
of terrain.
\item Pipelines are thought of as bi-directional. This assumption essentially
reflects the reality of pipelines. There are a few exceptional cases
where it is significantly more difficult to send water in one direction,
but these are rare enough that they can be disregarded.
\item Pipelines have variable rates of water transmission, depending on
factors such as size. In theory it would be possible to save money on pipelines by constructing smaller pipelines in areas where water rarely needs to be transported at high rates. 
However, the amount of water that needs to be transported through any given pipe is highly variable (ie. after a sudden intense rainfall). Thus, pipelines for long-distance water transmissions are relatively stable in cost. Our estimate below for pipeline cost is a typical figure.
\item Some pipelines exist already, but we do not consider them in our model. This is partially because they are likely to have minimal impact because there are not many of them, and partially because already-existing pipelines are poorly documented, so there is no way to efficiently collect and parse such data
\end{itemize}

@@

Based on the average cost of de-salinization facilities noted above, it would cost \$79 billion to build enough de-salinization plants to meet this demand.
